{\fontfamily{ptm}\selectfont Inexact Accelerated Proximal Gradient }

### 2025-10-03 Notebook LaTEX/Inexact AGP made simple for applications/main.tex
>w<, changes

            \item $(B_k)_{k \ge 0}$ is a non-negative sequence, characterizing any potential line search routine. 
            \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k > 0$, characterizing the over-relaxation of the proximal gradient operator. 
            \item $(\epsilon_k)_{k \ge 0}$ is a non-negative sequence characterizing the errors of inexact proximal evaluation.

@@

            \item $p \ge 1$ is some constant which will bound the error $\epsilon_k$ relative to $\rho_k$. 

@@

        In addition, we assume that the error parameter $\epsilon_k$ and over-relaxation parameter $\rho_k$, iterates $x_k, y_k$ and $\beta_k$ together satisfies for all $k \ge 0$ the relations:

@@

            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le (\rho_k/2)\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 

@@

                \item there exists $\bar x \in \RR^n$ that is an minimizer of $F = f + g$;
            Then, $\alpha_k \in (0, 1]$ hence valid and, it satisfies for all $k \ge 0$: 

@@

@@

@@

            Finally, since $p > 0$ the sum is convergent and hence it has an over all convergence rate $\mathcal O(1/k^2)$. 

@@

            From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_0^{-2}L_0^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities: 

@@

                \item $\beta_k$ is nonincreasing and $\beta_k > 0$ for all $k \ge 0$ because $\beta_k = \prod_{i = 1}^{k} (1 - \alpha_i)$ and, $\alpha_k \in (0, 1]$. 
                \item It has the equalities $\beta_k/\beta_{k - 1} = (1 - \alpha_k) = \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2 L_{k - 1}}$ for all $k \ge 1$. 

@@

            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem1}\begin{split}

@@

            \begin{align}\label{eqn:opt-cnvg-outr-loop-pitem2}\begin{split}

@@

            Combining \eqref{eqn:opt-cnvg-outr-loop-pitem1}, \eqref{eqn:opt-cnvg-outr-loop-pitem2} it would mean for all $i \ge 1$ it has: 

@@

@@

@@

                    2\beta_i^{-1/2}
                &= 4\left(
                \sqrt{\frac{L_0\alpha_0^2}{L_i}} &\le
                2 \left(

@@

@@

            Finally, one can solves for $\alpha_k$ by the recursive equality, and it should yield:

@@

@@

        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfies for all $k \ge 1$: 

@@

            Consider the proximal gradient inequality from \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality 

@@

            Hence for all $\bar x \in S$ it has 

@@

            Multiple bothside by $\frac{\gamma}{2\tau}$ then we are done. 

@@

        \end{proof}
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[inner loop linear convergence scenario 1]\label{prop:inn-loop-lin-cnvg}

>>>>

            \item $(B_k)_{k \ge 0}$ has $B_k > 0\; \forall k$, it characterizes any potential line search, back tracking routine. 
            \item $(\rho_k)_{k \ge 0}$ be a sequence such that $\rho_k \ge 0$, characterizing the over-relaxation of the proximal gradient operator. 
            \item $(\epsilon_k)_{k \ge 0}$ has $\epsilon_k > 0$ for all $k \ge 0$, it characterizes the errors of inexact proximal evaluation.

@@

            \item $p \ge 1$ is some constant which will bound the error $\epsilon_k$ relative to $\rho_k\Vert x_k - y_k\Vert^2, \beta_k$ and, $k$. 

@@

        In addition, we assume that the error parameter $\epsilon_k \ge 0$ and over-relaxation parameter $\rho_k$, iterates $x_k, y_k$ and $\beta_k$ together satisfies for all $k \ge 0$ the relations:

@@

            \item For all $k \ge 0$, it has $\frac{-\mathcal E_k}{k^p} \le \frac{\rho_k}{2}\Vert x_k - y_k\Vert^2 - \epsilon_k$ where $p \ge 1$, 

@@

        \begin{assumption}[the optimal momentum sequence]\;\label{ass:opt-mmntm-seq}\\
            Keeping everything assumed in Assumption \ref{ass:valid-err-schedule} about $(\alpha_k, B_k, \rho_k, \epsilon_k)_{k \ge 0}$, $(F, f, g, L)$, $(y_k, x_k, v_k)_{k \ge 0}$, $(\beta_k)_{k \ge 0}$, $\mathcal E_0$ and $p$, we assume in addition that the sequence $(\alpha_k)_{k \ge 0}$ satisfies for all $k \ge 0$ the equality: $(1 - \alpha_k) = \alpha_{k}^2L_k\alpha_{k - 1}^{-2}L_{k - 1}^{-1}$. 
        \begin{lemma}[the consequencse of optimal momentum sequence]\;\label{lemma:opt-mmntm-seq}\\
            Let $(\alpha_k)_{k \ge 0}, (\beta_k)_{k \ge 0}$ be given by Assumption \ref{ass:opt-mmntm-seq}, then $\forall k\ge 1\; \alpha_k \in (0, 1)$ and, in addition the sequence $(\beta_k)_{k \ge 0}$ has

@@

                    1 + \alpha_0\sqrt{L_0}\sum_{i = 1}^{k}\sqrt{L_i^{-1}}
                \hspace{-1em}\le 
                \beta_k

@@

                    1 + \frac{\alpha_0\sqrt{L_0}}{2}\sum_{i = 1}^{k}\sqrt{L_i^{-1}}

@@

@@

            Now, we focus on $(\beta_k)_{k \ge 0}$. 
            From the assumption that $(\alpha_k)_{k \ge 0}$ has $(1 - \alpha_k) = \alpha_k^2L_k \alpha_{k - 1}^{-2}L_{k - 1}^{-1}$ for all $k \ge 0$ and, the definition of $\beta_k$, it yields the following equalities: 

@@

                \item[(a)] $\beta_k$ is monotone decreasing and $\beta_k > 0$ for all $k \ge 0$ because $\beta_k = \prod_{i = 1}^{k} (1 - \alpha_i)$ and, $\alpha_k \in (0, 1]$. 
                \item[(b)] It has the equalities $\beta_k/\beta_{k - 1} = (1 - \alpha_k) = \frac{\alpha_k^2L_k}{\alpha_{k - 1}^2 L_{k - 1}}$ for all $k \ge 1$. 

@@

            \begin{align}\label{eqn:opt-mmntm-seq-pitem1}\begin{split}

@@

            \begin{align}\label{eqn:opt-mmntm-seq-pitem2}\begin{split}

@@

            Combining \eqref{eqn:opt-mmntm-seq-pitem1}, \eqref{eqn:opt-mmntm-seq-pitem2} it would mean for all $i \ge 1$ it has: 

@@

                &= \left(

@@

                \right)^2\left(
                    1 + \beta_i^{1/2}\beta_{i - 1}^{-1/2}
                \right)^2. 
            Since $\beta_i$ is monotone decreasing, it has $\beta_i^{-1/2}\beta_{i - 1}^{-1/2} \le 1$, and since $\alpha \in (0, 1)$
            \todoinline{HERE! IT'S NOT FINISHED YET!!!}
                \item there exists $\bar x \in \RR^n$ that is a minimizer of $F = f + g$;
                % \item the sequence $\rho_k$ must also recursively satisfies $\rho_k \ge \max\left(-B_k + \alpha_{k - 1}^4(\rho_{k - 1} + B_{k - 1}), 0\right)$. 
            Then, $\alpha_k \in (0, 1]\;\forall k \ge 0$ hence it's always valid and, it has $\forall k \ge 0$: 

@@

@@

            Since, $p > 0$ the sum is convergent and hence the above inequality claims an overall convergence rate $\mathcal O(1/k^2)$. 

@@

            Finally, one can solve for $\alpha_k$ by the recursive equality, and it should always have one of the strictly positive root: 
                \alpha_k &=
                \frac{L_{k - 1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \left(
                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
                    \right)^{1/2}
                &= \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
                    - 1 + \left(
                        1 + \frac{4 L_k}{L_{k - 1}\alpha_{k-1}^2}
                    \right)^{1/2}
                &\underset{(1)}{\le} \frac{\alpha_{k - 1}^2L_{k - 1}}{2L_k}\left(
                    - 1 + 1 + 2 \alpha_{k - 1}^{-2}\frac{L_k}{L_{k - 1}}
                &= 1
            At (1) we completed a square inside of the radical: 
                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
                1 + 4 L_{k}L_{k - 1}^{-1}\alpha_{k - 1}^{-2}
                + 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
                - 2L_k^2L_{k - 1}^{-2}\alpha_{k - 1}^{-4}
                &= (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2
                - 2\alpha_{k - 1}^{-4}L_k^2L_{k - 1}^{-2}
                &\le (1 + 2L_kL_{k - 1}^{-1}\alpha_{k - 1}^{-2})^2. 
            To see that $\alpha_k > 0$, recall that we had the assumption that $B_k > 0$ making $L_k > 0$. 
            If we inductively assume that $\alpha_{k - 1} \in (0, 1]$ then $\alpha_k > 0$ because: 
                \alpha_k &=
                \frac{L_{k - 1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \left(
                        \alpha_{k - 1}^4 + 4 \alpha_{k - 1}\frac{L_k}{L_{k - 1}}
                    \right)^{1/2}
                &\ge \frac{L_{k - 1}}{2L_k}\left(
                    - \alpha_{k - 1}^2 + \left(
                        \alpha_{k - 1}^4
                    \right)^{1/2}
                &> 0. 

@@

            In this remark, we assert the fact that all assumptions made in the theorem can be satisfied on practice, and we will also bring attention to the current, and future roles played by each of the parameters used in the inexact algorithm. 
            Pay close attention that $\alpha_k$ had been determined in the above theorem, and $(B_k)_{k \le 0}$ is reserved for potential line search routine, the only parameter left undetermined in Definition \ref{def:inxt-apg} is the over-relaxation sequence $(\rho_k)_{k \ge 0}$, we only need the entire sequence is bounded above. 
            We give the freedom to the practitioners to choose $(\rho_k)_{k \ge 0}$. 
            However, this sequence $\rho_k$ is not useless because it relaxes the upper bound for $\epsilon_k$, this has huge impact in the earlier stage (the first few iterations) of the algorithm $\Vert x_k - y_k\Vert$ is large. 
            Of course, the parameter $\mathcal E_0$ is also free to choose. 
            The the next subsection, we will show that under the assumption of the above theorem, there exists an error sequence $\epsilon_k$ such that it can never approach $0$ at an arbitrarily fast rate. 
    \subsection{the fastest rate of which the error schedule can shrink}
        To have overall convergence claim of the algorithm, it's necessary to prevent the error schedule $(\epsilon_k)_{k \ge 0}$ from crashing into zero too quickly. 
        Following Assumption \ref{ass:valid-err-schedule}, in this section, we will provide the lower bound results for $\epsilon_k$ in Theorem \ref{prop:opt-cnvg-outr-loop} to show that in the worst case it cannot approach zero arbitrarily fast, if we choose the largest possible $\epsilon_k$ using $\beta_k$.

@@

        Then an algorithm is a proximal gradient method if it generates iterates $(x_k)_{k \ge 0}$ such that they satisfy for all $k \ge 1$: 

@@

            Consider the proximal gradient inequality from Theorem \ref{thm:inxt-pg-ineq}, but with $\rho = 0, \epsilon = 0, B = \tau$, then for all $x$ such that $\Vert \mathcal G_\tau(x)\Vert > 0$ it has for $\tilde x = T_{\tau}(x), z \in \RR^n$ the inequality 

@@

            Hence, for all $\bar x \in S$ it has 

@@

            Multiple both side by $\frac{\gamma}{2\tau}$ then we are done. 

@@

        \end{proof}
        \par
        The following propositions precisely show that the linear convergence is achievable for the inner loop when $g = \Vert \cdot\Vert_1$ for our optimization objective. 
        \begin{proposition}[inner loop linear convergence scenario 1]\label{prop:inn-loop-lin-cnvg}
